BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-18 tex/5-evaluation.tex
Remove 5.3, move related work before the conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preservation of blog visuals}
\TODO{visuals/design/graphic/?}

Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}. Our final solution consists in taking a screenshot with our embeded web browser after the JavaScript rendering. Before opting for this approach, we considered 3 other solutions: GNU Wget, wkhtmltopdf and OXPath. This subsection relates our evaluation of these tools for the specific purpose.

The first solution we considered was the GNU/Linux tool wget. With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images). On simple webpages, this process effectively captures all files necessary to display the page locally. However, it falls short* to capture webpages that download content via javascript.

Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages. It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.

The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling. It also make use of a complete web browser to render pages and execute page interactions sequentially. OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.

\savevisualsTable

\TODO{}

>>>>

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Preservation of blog visuals}
% \TODO{visuals/design/graphic/?}

% Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}. Our final solution consists in using the embeded web browser to take screenshots after each page rendering. Before opting for this approach we considered 3 other solutions: GNU wget, wkhtmltopdf and OXPath. This subsection relates our evaluation of these tools for the specific purpose.

% \TODO{Is this whole subsection legitimate? It this part is not really relevant we could also simply not include it... I guess it is not a really useful from a research point of vue, but it might still be of some use for others to know what each of them can do. I think it's also important to say at some point how long it takes to render a pages, because if only look at the graph it seams like this is all super fast, but when we use PhantomJS the thing seriously slows down...}

% The first solution we considered was the GNU/Linux tool wget. With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images). On simple webpages, this process effectively captures all files necessary to display the page locally. However, it falls short* to capture webpages that download content via javascript.

% Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages. It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.

% The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling. It also make use of a complete web browser to render pages and execute page interactions sequentially. OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.

% \savevisualsTable

### 2014-01-18 tex/main.tex
Intro almost done, RSS left
Into on RSS almost done, some issues to compile w latexmk
Added related work on large scale distributed crawlers$
Remove 5.3, move related work before the conclusion

\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
\renewcommand\comment[1]{\emph{\color{Gray}<#1>}}
\newcommand\edit[1]{\emph{\color{Green}<#1>}}
\newcommand\code[1]{\texttt{#1}}
\newcommand\coderef[1]{\texttt{\ref{#1}}}
\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
\newcommand\len[1]{|#1|}
\newcommand\set[1]{\{#1\}}
\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
\newcommand\Oof[1]{$\mathcal{O}(#1)$}

@@

  % % A category with the (minimum) three required fields
  % \category{H.4}{Information Systems Applications}{Miscellaneous}
  % %A category including the fourth, optional field follows...
  % \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

  \terms{Algorithms, Software Engineering}

  \keywords{Web crawling, Web Data Extraction, Wrapper Generation, Web archiving, ...}

  \input{algos.tex}
  \input{tables.tex}
  \input{1-intro.tex}
  \input{2-related-work.tex}
  \clearpage
  \input{3-algorithms.tex}
  \clearpage
  \input{4-techniques.tex}
  \clearpage
  \input{5-evaluation.tex}
  \clearpage
  \input{6-conclusion-and-future-work.tex}

>>>>

\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
\renewcommand\comment[1]{\emph{\color{Gray}#1}}
\newcommand\code[1]{\texttt{#1}}
\newcommand\coderef[1]{\texttt{\ref{#1}}}
\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
\newcommand\len[1]{|#1|}
\newcommand\set[1]{\{#1\}}
\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
\newcommand\Oof[1]{$\mathcal{O}(#1)$}

@@

  ~\\\TODO{I'm for including the first two categories:}

  \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}[Information filtering, Selection process]
  \category{\\D.2.8}{Software Engineering}{Metrics}[Complexity measures, Performance measures]
  \category{\\H.3.7}{Information Storage and Retrieval}{Digital Libraries}[Collection]
  \category{\\H.3.4}{Information Storage and Retrieval}{Systems and Software}[Performance evaluation]

  % In order of most significant, first letter of each word capitalized.
  \terms{Design, Algorithms, Performance, Experimentation}

  % In alphabetical order, first letter of the first word capitalized.
  \keywords{Blog crawler, wrapper generation, web data extraction}

  \input{algos.tex}
  \input{tables.tex}
  ~\\
  \input{1-intro.tex}
  \clearpage
  \input{3-algorithms.tex}
  \clearpage
  \input{4-techniques.tex}
  \clearpage
  \input{5-evaluation.tex}
  \clearpage
  \input{2-related-work.tex}
  \clearpage
  \input{6-conclusion-and-future-work.tex}
